---
---
title: "Regression"
output: html_document
---
Downloading the packages and loading them and importing my csv!
```{r}
install.packages(c(
  "dplyr",
  "tidyverse",
  "estimatr",
  "stargazer",
  "readr",
  "stringr"
))
library(dplyr)
library(tidyverse)
library(estimatr)
library(stargazer)
library(readr)
library(stringr)

murder <- read_csv("murderpedia_updated.csv")
head(murder)

```
Next I will be making Gender, Violent, Serial Killer, Shooting, and USA into Binary Variables. I am also converting victim number into a numeric.
```{r}
# Male = 1, Female = 0
murder$male_binary <- ifelse(
  murder$gender == "Male", 1, 0
)

# Violent = 1, Non-violent = 0
murder$violent_binary <- ifelse(
  murder$violent_vs_nonviolent == "Violent", 1, 0
)

# Serial killer = 1, Not serial killer = 0
murder$serial_killer_binary <- ifelse(
  murder$serial_killer == "Yes", 1, 0
)

# USA = 1, Non-USA = 0
murder$usa_binary <- ifelse(
  murder$usa_location == "USA", 1, 0
)

# Creating shooting binary variable
murder$shooting_binary <- ifelse(
  murder$method == "Shooting", 1, 0
)
# Creating numeric victim variable https://www.geeksforgeeks.org/r-language/as-numeric-function-in-r/ 
murder$victims_num <- as.numeric(
  str_extract(murder$victims, "\\d+")
)

head(murder)
```
My first regression will be an Ols examining whether males are more likely to use violent methods and whether the relationship changes depending on the location.
```{r}
reg1 <- lm(
  violent_binary ~ male_binary * usa_binary,
  data = murder
)

summary(reg1)
```
# Regression 2: Male Serial Killer Interaction

This regression is also an OLs and examines whether male serial killers and USA location are associated with using violent methods.

```{r}
reg2 <- lm(
  violent_binary ~ male_binary * serial_killer_binary + usa_binary,
  data = murder
)

summary(reg2)
```

# Regression 3: Shooting Logit Model

This regression estimates the probability of using shooting as a homicide method. Since shooting is a binary outcome (shooting or not shooting), I will be using a Logit Model.

First I need to install the margins package before I run it. 
After that is done I will run my logit regression and be using the average marginal effects.
```{r}
install.packages("margins")
library(margins)

# Running logit model
reg3 <- glm(
  shooting_binary ~ male_binary + usa_binary + serial_killer_binary,
  data = murder,
  family = "binomial"
)

# Average marginal effects
margins(reg3)

# Marginal effects at USA = 1
margins(
  reg3,
  at = list(usa_binary = 1)
)

# Marginal effects at USA = 0
margins(
  reg3,
  at = list(usa_binary = 0)
)

# Regression summary
summary(reg3)
```
Lastly, I will be adding all my regressions into a html table!
```{r}
stargazer(
  reg1, reg2, reg3,
  
  type = "html",
  out = "regression_table.html",
  
  title = "Regression Results",
  
  column.labels = c(
    "Violent (USA)",
    "Violent (Serial Killer)",
    "Shooting (AME)"
  ),
  
  dep.var.labels.include = FALSE,
  
  covariate.labels = c(
    "Male",
    "Serial Killer",
    "USA",
    "Male * USA",
    "Male * Serial Killer"
  ),
  
  model.names = FALSE,
  
  digits = 3
)
```